Segregation in Vienna's primary schools?

### 2021-01-13 _post/2020-03-02-primary-schools-in-vienna/primary-schools-in-vienna.Rmd
modified post on primary schools; theme;

theme: theme.css

@@

library(tidyverse)
library(ggplot2)
library(here)
library(extrafont)
loadfonts(device = "win", quiet = T)
extrafont::fonts()
library(hrbrthemes)
library(scales)
library(ggiraph)
library(knitr)
library(mapdeck)
library(widgetframe)
library(htmlwidgets)
library(plotly)
library(paletteer)
library(ggtext)
library(janitor)
library(magrittr)
options(digits = 12)
options(pillar.sigfig = 12)
library(geosphere)
library(plotly)
library(crosstalk)
```

```{r setup, echo = F}
# knit_hooks$set(wrap = function(before, options, envir){
# if (before){
# paste0('<', options$wrap, '>')
# } else {
# paste0('</', options$wrap, '>')
# }
# })
knitr::opts_chunk$set(warning = FALSE, message = FALSE, dpi = 180, fig.height = 5, fig.width = 7, fig.align = "center")
options(width = 180, dplyr.width = 150)

@@

```{r, eval=T}
# add details of schools to dataframe containing all combinations of schools (nested);
# first for 1st school in pair, then for 2nd school in pair;
# extract values of interest for easier handling from nested dataframe;
df_main <- df_difference %>%
  mutate_at(vars("school_1", "school_2"), as.numeric) %>%
  nest_join(., df_primary_schools_vienna,
    by = c("school_1" = "properties_skz")
  ) %>%
  rename(school_1_details = df_primary_schools_vienna) %>%
  mutate(school_1_lat = map_dbl(school_1_details, purrr::pluck, "lat")) %>%
  mutate(school_1_long = map_dbl(school_1_details, purrr::pluck, "long")) %>%
  # nest(school_1_coords=c(school_1_lat, school_1_long)) %>%
  nest_join(., df_primary_schools_vienna,
    by = c("school_2" = "properties_skz")
  ) %>%
  rename(school_2_details = df_primary_schools_vienna) %>%
  mutate(school_2_lat = map_dbl(school_2_details, purrr::pluck, "lat")) %>%
  mutate(school_2_long = map_dbl(school_2_details, purrr::pluck, "long")) %>%
  mutate(address1 = map(school_1_details, ~ .x %>% mutate(school_1_address = paste(properties_bezeichnung,
    properties_str,
    properties_plz,
    sep = ", "
  ))) %>%
    map_chr(., purrr::pluck, "school_1_address")) %>%
  mutate(address2 = map(school_2_details, ~ .x %>% mutate(school_2_address = paste(properties_bezeichnung,
    properties_str,
    properties_plz,
    sep = ", "
  ))) %>%
    map_chr(., pluck, "school_2_address")) %>%
  mutate(school_1_erhalter = map(school_1_details, purrr::pluck, "properties_erhalter")) %>%
  mutate(school_2_erhalter = map(school_2_details, purrr::pluck, "properties_erhalter")) %>%
  mutate(school_erhalter_indicator = map2_chr(
    school_1_erhalter, school_2_erhalter,
    function(x, y) paste(pmin(x, y), pmax(x, y), sep = "-")
  )) %>%
  mutate(school_1_erhalter = map(school_1_details, extract, "properties_erhalter") %>% unlist()) %>%
  mutate(school_2_erhalter = map(school_2_details, extract, "properties_erhalter") %>% unlist()) %>%
  mutate(erhalter_type = paste(school_1_erhalter, school_2_erhalter, sep = " - ")) %>%
  left_join(., df_share %>%
    filter(school_type_secondary == "matura") %>%
    select(school_1_n_rel = n_rel, properties_skz_vj),
  by = c("school_1" = "properties_skz_vj")
  ) %>%
  left_join(., df_share %>%
    filter(school_type_secondary == "matura") %>%
    select(school_2_n_rel = n_rel, properties_skz_vj),
  by = c("school_2" = "properties_skz_vj")
  )

# readr::write_rds(df_main, file=here::here("_blog_data", "Vienna_primary_schools","df_main2.rds"))

@@

cross_map2 <- plotly::plot_mapbox(
  data = shared_df_main,
  hoverinfo = "text",
  text = ~ paste(
    "abs diff AHS ratio (% points):", round((diff_abs * 100), 2),
    "</br>AHS factor:", round(diff_factor, 2),
    "</br>distance (m):", round(distance, 0),
    "</br>", tooltip
  )
) %>%
  plotly::add_markers(
    y = ~school_1_lat,
    x = ~school_1_long,
    color = "#FF0000" #,
    # text = ~address1
  ) %>%
  plotly::add_markers(
    y = ~school_2_lat,
    x = ~school_2_long,
    color = "#FF0000" # ,
    # text = ~address2
  ) %>%
  layout(
    mapbox = list(
      style = "mapbox://styles/zoowalk/ckjrkv7065tf519oax4nadm2k",
      margin=list(l=0,r=0,t=0,b=0,p=0),
      zoom = 10,
      center = list(
        lat = 48.21,
        lon = 16.3720798
      )
    ),
    showlegend = FALSE,
    paper_bgcolor = bgr_color
  ) %>% 
    config(mapboxAccessToken = Sys.getenv("MAPBOX_TOKEN"))
```
</details>

```{r, eval=T}
# combine graphs

cross_plot <- crosstalk::bscols(
plot_distance_diff,
cross_map2)
#

cross_plot <- crosstalk::bscols(
plot_distance_diff,
cross_map2)
```{r eval=FALSE, include=FALSE}
# cross_plot
```

cross_plot <- browsable(tagList(cross_plot))
cross_plot

```{r, eval=T}
library(htmltools)
# cross_plot <- browsable(tagList(plot_distance_diff, cross_map2))
cross_plot <- browsable(tagList(cross_plot))
# cross_plot
```

```{r, eval=T}
# see here for how to remove bootstrap css which otherwise messes up you blogdown's css
# https://github.com/rstudio/crosstalk/issues/26

@@

cross_plot_clean <- unstrap(cross_plot)
```

cross_plot_clean
```{r echo=FALSE, layout="l-page", fig.height=30}

>>>>

@@

library(tidyverse)
library(ggplot2)
library(here)
library(extrafont)
loadfonts(device = "win", quiet = T)
library(hrbrthemes)
library(scales)
library(ggiraph)
library(knitr)
library(mapdeck)
library(widgetframe)
library(htmlwidgets)
library(plotly)
library(paletteer)
library(ggtext)
library(janitor)
library(magrittr)
options(digits = 12)
options(pillar.sigfig = 12)
library(geosphere)
library(plotly)
library(crosstalk)
library(htmltools)
```

```{r setup, echo = F}

knitr::opts_chunk$set(warning = FALSE, message = FALSE, dpi = 180, fig.height = 5, fig.width = 7, fig.align = "center")
options(width = 180, dplyr.width = 150)

@@

```{r, eval=F}
# add details of schools to dataframe containing all combinations of schools (nested);
# first for 1st school in pair, then for 2nd school in pair;
# extract values of interest for easier handling from nested dataframe;
df_main <- df_difference %>%
  mutate_at(vars("school_1", "school_2"), as.numeric) %>%
  nest_join(., df_primary_schools_vienna,
    by = c("school_1" = "properties_skz")
  ) %>%
  rename(school_1_details = df_primary_schools_vienna) %>%
  mutate(school_1_lat = map_dbl(school_1_details, purrr::pluck, "lat")) %>%
  mutate(school_1_long = map_dbl(school_1_details, purrr::pluck, "long")) %>%
  # nest(school_1_coords=c(school_1_lat, school_1_long)) %>%
  nest_join(., df_primary_schools_vienna,
    by = c("school_2" = "properties_skz")
  ) %>%
  rename(school_2_details = df_primary_schools_vienna) %>%
  mutate(school_2_lat = map_dbl(school_2_details, purrr::pluck, "lat")) %>%
  mutate(school_2_long = map_dbl(school_2_details, purrr::pluck, "long")) %>%
  mutate(address1 = map(school_1_details, ~ .x %>% mutate(school_1_address = paste(properties_bezeichnung,
    properties_str,
    properties_plz,
    sep = ", "
  ))) %>%
    map_chr(., purrr::pluck, "school_1_address")) %>%
  mutate(address2 = map(school_2_details, ~ .x %>% mutate(school_2_address = paste(properties_bezeichnung,
    properties_str,
    properties_plz,
    sep = ", "
  ))) %>%
    map_chr(., pluck, "school_2_address")) %>%
  mutate(school_1_erhalter = map(school_1_details, purrr::pluck, "properties_erhalter")) %>%
  mutate(school_2_erhalter = map(school_2_details, purrr::pluck, "properties_erhalter")) %>%
  mutate(school_erhalter_indicator = map2_chr(
    school_1_erhalter, school_2_erhalter,
    function(x, y) paste(pmin(x, y), pmax(x, y), sep = "-")
  )) %>%
  mutate(school_1_erhalter = map(school_1_details, extract, "properties_erhalter") %>% unlist()) %>%
  mutate(school_2_erhalter = map(school_2_details, extract, "properties_erhalter") %>% unlist()) %>%
  mutate(erhalter_type = paste(school_1_erhalter, school_2_erhalter, sep = " - ")) %>%
  left_join(., df_share %>%
    filter(school_type_secondary == "matura") %>%
    select(school_1_n_rel = n_rel, properties_skz_vj),
  by = c("school_1" = "properties_skz_vj")
  ) %>%
  left_join(., df_share %>%
    filter(school_type_secondary == "matura") %>%
    select(school_2_n_rel = n_rel, properties_skz_vj),
  by = c("school_2" = "properties_skz_vj")
  )

# readr::write_rds(df_main, file=here::here("_blog_data", "Vienna_primary_schools","df_main_base.rds"))

```{r, eval=T, include=F}
df_main <- readr::read_rds(here::here("_blog_data", "Vienna_primary_schools", "df_main_base.rds"))

@@

cross_map2 <- plotly::plot_mapbox(
  data = shared_df_main,
  hoverinfo = "text",
  text = ~ paste(
    "abs diff AHS ratio (% points):", round((diff_abs * 100), 2),
    "</br>AHS factor:", round(diff_factor, 2),
    "</br>distance (m):", round(distance, 0),
    "</br>", tooltip
  )
) %>%
  plotly::add_markers(
    y = ~school_1_lat,
    x = ~school_1_long,
    color = "#FF0000" #,
    # text = ~address1
  ) %>%
  plotly::add_markers(
    y = ~school_2_lat,
    x = ~school_2_long,
    color = "#FF0000" # ,
    # text = ~address2
  ) %>%
  layout(
    mapbox = list(
      style = "mapbox://styles/zoowalk/ckjrkv7065tf519oax4nadm2k",
      margin=list(l=0,r=0,t=0,b=0,p=0),
      zoom = 10,
      center = list(
        lat = 48.21,
        lon = 16.3720798
      )
    ),
    showlegend = FALSE,
    paper_bgcolor = bgr_color
  ) %>% 
    config(mapboxAccessToken = Sys.getenv("MAPBOX_TOKEN"))

#combine both plots vertically/as two columns
#problem: introduces bootstrap css which conflicts with css of blog
cross_plot <- crosstalk::bscols(plot_distance_diff, cross_map2)

cross_plot <- browsable(tagList(cross_plot))

# see here for how to remove bootstrap css which otherwise messes up you blogdown's css
# https://github.com/rstudio/crosstalk/issues/26
# only works when combining plots vertically though ! hence css not as intended;

@@

cross_plot_clean <- unstrap(cross_plot)
```
</details>

```{r echo=FALSE, fig.height=30, layout="l-page"}
